---
title: "data cleaning"
author: "BR"
date: "17/02/2020"
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(rqdatatable)
library(gtools)
```

```{r}
raw_df<-read_csv("kobo_response.csv") %>% 
  select_if(function(x){!all(is.na(x))}) %>% 
  mutate(survey_date=as.Date(survey_date, "%Y, %m, %d"))

names(raw_df) <- gsub(x = names(raw_df), pattern = "^_", replacement = "q")  
names(raw_df) <- gsub(x = names(raw_df), pattern = "/", replacement = "_") 

master_id<-read_csv("master_survey_resp_copy.csv") %>% 
  select(start, survey_id, country, community) %>% 
  mutate(new_id = survey_id) %>% 
  select(-survey_id) %>% 
  mutate(community = ifelse(community=="TTN", "ALT", community))

```


Last surveys from ind
```{r}
last_ind<-read_csv("Tracking Tech Survey (IND).csv") %>%
  select(-community, -country) %>% 
  left_join(master_id) %>% 
  mutate(survey_id = new_id) %>% 
  mutate(community = ifelse(survey_id > 8000, "JPR", "WKB"), 
         country = "IND")

#names(last_ind)
```

Reassigning survey_id

1.COUNTRY & 2. COMMUNITY 

```{r}
#com_fix & country_fix
old_community<-unique(raw_df$community)
community_fix<-c("RAJ","RAJ", NA, NA,"RAJ","RAJ", "RAJ","RAJ", "MNC","MAK", "MAK", "MAK", "MAK","MAK", "MAK","MAK","MNC", "MNC","PSC", "ALT", "ALT", "WKB", "WKB")

country_df<-data.frame(com_fix = c("RAJ", "MAK", "MNC", "PSC", "ALT", "WKB", "JPR"), country_fix = c("IND", "IND", "IND", "MEX", "MEX", "IND", "IND"))

community_df<-data.frame(community = old_community, com_fix = community_fix) %>% 
  left_join(country_df) %>% 
  right_join(raw_df) %>% 
  mutate(country_fix=as.character(country_fix))

community_na<-community_df %>% 
  filter(country_fix %in% NA) %>% 
  mutate(country_fix = ifelse(country=="indonesia", "IND", 
                              ifelse(country=="mexico", "MEX", country_fix))) %>% 
  mutate(country_fix = ifelse(is.na(country_fix), "MEX", country_fix)) %>% #correction made based on survey dates
  separate(survey_date, c("year", "month", "date"), "-", extra = "merge", convert = TRUE) %>% 
  mutate(com_fix = ifelse(date>10, "ALT", com_fix)) %>% 
  mutate(com_fix=ifelse(country_fix=="IND", "RAJ",
                        ifelse(is.na(com_fix), "PSC", com_fix))) %>% 
  select(start, com_fix, country_fix)

location_df<-natural_join(community_df, community_na, by = "start",jointype = "FULL") %>% 
  mutate(country=ifelse(country_fix=="1", "IND",
                        ifelse(country_fix=="2", "MEX", country_fix))) %>% 
  mutate(community=com_fix) %>% 
  select(start, community, country)

survey_pre_psc<-raw_df %>%
  select(-community, -country) %>% 
  left_join(location_df) %>% 
  subset(select=c(1:5,324:325, 6:323))
```

Intro questions 
"start"
"end"
"survey_type"
"survey_id"
"survey_date"
"survey_time"
"survey_version"
"interviewer"
"country"
"community"
"sex"

```{r}
intro<-survey %>% 
  select("start",
          "end",
          "survey_type",
          "survey_id",
          "survey_date",
          "survey_time",
          "survey_version",
          "interviewer",
          "country",
          "community",
          "sex")
```


making corrections for PSC data
There should be 46 surveys 
```{r}
psc<-survey_pre_psc %>% 
  rename(old_id = survey_id) %>% #renaming to avoid problems when joining 
  left_join(master_id) %>% # joining with final assigned survey id's
  filter(community == "PSC")

psc_old<-psc %>% #filtering the incorrect portions 
  select(-c(choice_001:wtr_4), - old_id) %>% 
  rename(survey_id = new_id) 

#All correct, corrections
psc_fix<- psc  %>% 
  filter(is.na(new_id)) %>% #filter for the surveys that are the corrections 
  select(old_id, survey_version, interviewer, c(choice_001:wtr_4)) %>% 
  rename(survey_id = old_id, fisher = interviewer) %>% 
  mutate(survey_id = as.numeric(survey_id)) %>%
  filter(!is.na(survey_id)) %>% 
  left_join(psc_old) %>% 
  distinct(survey_id, .keep_all = TRUE) %>% 
  mutate(interviewer = fisher) %>% 
  select(-fisher) 

psc_good<-psc %>%
  filter(is.na(old_id)) %>% 
  select(start) %>% 
  left_join(psc_fix, by = "start") %>% 
  filter(is.na(survey_id)) %>%
  select(start) %>%
  left_join(raw_df) %>%
  select(-survey_id, -community, -country) %>% 
  left_join(master_id) %>% 
  rename(survey_id = new_id)

psc_final<-rbind(psc_fix, psc_good) 
```

```{r}
survey<-survey_pre_psc %>% 
  filter(community!="PSC") %>%
  select(-survey_id) %>% 
  left_join(master_id) %>% 
  rename(survey_id = new_id) %>% 
  rbind(psc_final) %>% 
  subset(select=c(325, 1:324)) %>% 
  filter(!is.na(country)) %>% 
  mutate(survey_id = ifelse(is.na(survey_id) & community == "ALT", 6042, survey_id)) #forgot to assign the last one
```

4. In the last 12 months, what fishing gear have you used? (Select all that apply)
⬜	Hand Line
⬜	Spear
⬜	Traps
⬜	Gill Net
⬜	Mobile Net (e.g., trawl, purse seine, beach seine)
⬜	Stationary Line (e.g. long line)
⬜	Other  ___________________________

*Adding Buceo
```{r}
#gear (13:21) & fishing_gear (169:176)
gear_df<-survey %>% 
  select(start, country, community, survey_id, c(14:21,170:177)) %>%
  mutate(other_gear = ifelse(is.na(other_4), gear_other, other_4)) %>% 
  mutate(gear_handline = ifelse(is.na(gear_hand_line), fishing_gear_hand_line, gear_hand_line), 
         gear_spear = ifelse(is.na(gear_spear), fishing_gear_spear, gear_spear),
         gear_traps = ifelse(is.na(gear_traps), fishing_gear_traps, gear_traps),
         gear_gillnet = ifelse(is.na(gear_gill_net), fishing_gear_gill_net, gear_gill_net),
         gear_mobilenet = ifelse(is.na(gear_mobile_net), fishing_gear_mobile_net, gear_mobile_net),
         gear_statline = ifelse(is.na(gear_stationary_line), fishing_gear_stationary_line, gear_stationary_line),
         gear_other = ifelse(is.na(gear_other_gear), fishing_gear_other, gear_other_gear)) %>%
  mutate(gear_buceo = ifelse(grepl("buceo", other_gear, ignore.case=TRUE), 1, 0)) %>% 
  mutate(gear_gillnet = ifelse(grepl("gillnet", other_gear, ignore.case = TRUE), 1 , gear_gillnet)) %>% 
  select(survey_id, gear_handline, gear_spear, gear_traps, gear_gillnet, gear_mobilenet, gear_statline, gear_other, gear_buceo, other_gear) 
```


5. For fishing purposes, do you own a boat, share a boat, or rent a boat from others, or do not use a boat?
6. For your primary fishing vessel, please describe the boat in the following aspects:


```{r}
vessel_df<-survey %>%
  mutate(boat_length = ifelse(is.na(boat_length), boat_length_m, boat_length)) %>% 
  select(survey_id, contains("boat"), -boat_length_m) %>% 
  mutate(boat_material =  ifelse(grepl("ka", boat_material, ignore.case=TRUE), "wood",
                                 ifelse(grepl("fib", boat_material, ignore.case = TRUE), "fiberglass", boat_material)))
```



7. What types of technology that you use at least once a week? (Select all that apply)
⬜	Smart-phone with Internet connection
⬜	Google Maps or other GPS apps
⬜	Twitter, Facebook, Instagram, or other social media
⬜	Other  ___________________________
⬜	None


```{r}
tech_df<- survey %>% 
  select(survey_id, c(29:34,180:186)) %>% 
  mutate(other_tech = ifelse(is.na(tech_other), Please_specify_other_001, tech_other),
         other_tech = ifelse(is.na(tech_other), other_07, tech_other), 
         tech_smartphone = ifelse(is.na(tech_smartphone), tech_use_smartphone, tech_smartphone),
         tech_maps = ifelse(is.na(tech_maps), tech_use_maps, tech_maps),
         tech_sm = ifelse(is.na(tech_socialmedia), tech_use_socialmedia, tech_socialmedia),
         tech_other = ifelse(is.na(tech_other_tech), tech_use_other, tech_other), 
         tech_none = ifelse(is.na(tech_no_tech), tech_use_none, tech_no_tech)) %>% 
  select(survey_id, tech_smartphone, tech_maps, tech_sm, tech_other, tech_none, other_tech)
```

8. 8. Which of these  types of technology do  you use/  have used at some point for your fishing activity (Select all that apply)
⬜	VHF radio
⬜	Fish Finder
⬜	Surveillance camera
⬜	Catch and data collection app
⬜	Vessel tracking technology
⬜	GPS
⬜	Other  ___________________________
⬜	None

```{r}
fishtech_df<- survey %>% 
  select(survey_id, c(35:49,187:196)) %>% 
  select(-fish_tech_socialmedia) %>%  #coding 
  #mutate(fish_tech = ifelse(is.na(fish_tech), fish_tech_use, fish_tech)) %>% 
  mutate(other_fishtech = ifelse(is.na(fish_tech_other), other_8, fish_tech_other)) %>% #other 1 of 2
  mutate(other_fishtech = ifelse(is.na(other_fishtech), other_08, other_fishtech)) %>%  #other 2/2
  mutate(fishtech_none = ifelse(is.na(fish_tech_no_fish_tech), fish_tech_use_none, fish_tech_no_fish_tech)) %>% #none
  mutate(fishtech_vhf = ifelse(is.na(fish_tech_vhf), fish_tech_use_vhf, 
                               ifelse(grepl("Radio", other_fishtech, ignore.case=TRUE), 1, fish_tech_vhf))) %>% #VHF radio
  mutate(fishtech_fishfiner = ifelse(is.na(fish_tech_fishfinder), fish_tech_use_fishfinder, fish_tech_fishfinder)) %>% #Fish Finder
  mutate(fishtech_survcam = ifelse(is.na(fish_tech_survcam), fish_tech_use_survcam, fish_tech_survcam)) %>% #Surveillance camera
  mutate(fishtech_catchapp = ifelse(is.na(fish_tech_catchapp), fish_tech_use_catchapp, fish_tech_catchapp)) %>% #Catch and data collection app
  mutate(fishtech_vms = ifelse(is.na(fish_tech_vesseltrack), fish_tech_use_vesseltrack, 
                               ifelse(grepl("pds", other_fishtech, ignore.case=TRUE), 1, fish_tech_vesseltrack))) %>% #vessel tracking technology
  mutate(fishtech_gps = ifelse(grepl("GPS", other_fishtech, ignore.case=TRUE), 1, 
                               ifelse(fishtech_none == 1, 0, fish_tech_gps))) %>% #GPS 
  mutate(fishtech_other = ifelse(is.na(fish_tech_other_fish_tech), fish_tech_use_other, fish_tech_other_fish_tech)) %>% #Other binary

  select(survey_id, fishtech_vhf, fishtech_fishfiner, fishtech_survcam, fishtech_catchapp, fishtech_gps, fishtech_vms, fishtech_other,fishtech_none, other_fishtech) %>%
  mutate(row_sum = apply(is.na(.), 1, sum)) %>% 
  mutate_if(is.numeric, funs(ifelse(is.na(.) & row_sum <9 , 0, .))) %>% 
  select(-row_sum)
```

9. What type of tracking technology did you use on your vessel?
10. Please list some positive aspects of this technology
11. Please list some negative aspects of this technology
*text*

```{r}
vms_text_df<- survey %>% 
  select(survey_id, tracking_tech, c(50:53,197:200)) %>% 
  mutate(positive_tracking_tech_one = ifelse(is.na(positive_tracking_tech_one), positive_one, positive_tracking_tech_one),
         positive_tracking_tech_two = ifelse(is.na(positive_tracking_tech_two), positive_two, positive_tracking_tech_two),
         negative_tracking_tech_one = ifelse(is.na(negative_tracking_tech_one), negative_one, negative_tracking_tech_one),
         negative_tracking_tech_two = negative_two) %>%
  rename(text_vms = tracking_tech) %>% 
  select(survey_id, text_vms, positive_tracking_tech_one, positive_tracking_tech_two, negative_tracking_tech_one, negative_tracking_tech_two)


```

12. You have to install and use one or the other tracking package for a year. Which would you be more likely to install and use consistently on every fishing trip?
◯  	Package One
◯ 	Package Two
13. Would you prefer the package you chose or no tracking package at all?
◯ 	Package Chosen
◯ 	No Package

14. wtp
15. wtr

```{r}
ce_df<- survey %>% 
  select(survey_id, c(54:64)) %>% 
  mutate(choice = ifelse(is.na(choice), choice_001, choice)) %>% 
  select(-choice_001)
```

16. Please mention any negatives that this technology might bring to you.

17. Please mention any other positives that this technology might bring to you.

19. Do you think you and your community would adopt this technology? Why or Why Not?
```{r}
vms_goodbad_df<- survey %>% 
  select(survey_id, c(65:66, 77, 220)) %>% 
  mutate(vms_adoption_text = ifelse(is.na(vms_adoption_text), tracking_adoption, vms_adoption_text)) %>% 
  select(-tracking_adoption)
```

18. Please choose 3 benefits you want from the tracking device, if it is installed in your boat. (Select three)
⬜	Data to help obtain a sustainable seafood certification
⬜	On-board Internet access
⬜	On-board electrical power for charging cell phones and other electronics
⬜	Text messaging services
⬜	Detailed tracking information for your vessel (e.g., drop pin in specific location)
⬜	Opportunities to acquire new tools and technical capacity (e.g. workshops for computer use)
⬜	Reduce illegal, unreported, and unregulated fishing in your fishing area
⬜	Increase in the monitoring capacity of the fishing association
⬜	Full data reports to show compliance with fishing authorities (e.g. monthly reports with fishing activity information, paired with catch data)


```{r}
ce_followup_df<-survey %>% 
  select(survey_id, c(67:76, 201:219)) 
  
names(ce_followup_df) <- gsub(x = names(ce_followup_df), pattern = "vms_design_vms_design_", replacement = "vms_design_")
names(ce_followup_df) <- gsub(x = names(ce_followup_df), pattern = "q1st_choice_", replacement = "choice_")

vms_design_df <- ce_followup_df %>% 
  mutate(vms_design_a = ifelse(is.na(vms_design_a), choice_a, vms_design_a),
         vms_design_b = ifelse(is.na(vms_design_b), choice_b, vms_design_b),
         vms_design_c = ifelse(is.na(vms_design_c), choice_c, vms_design_c),
         vms_design_d = ifelse(is.na(vms_design_d), choice_d, vms_design_d),
         vms_design_e = ifelse(is.na(vms_design_e), choice_e, vms_design_e),
         vms_design_f = ifelse(is.na(vms_design_f), choice_f, vms_design_f),
         vms_design_g = ifelse(is.na(vms_design_g), choice_g, vms_design_g),
         vms_design_h = ifelse(is.na(vms_design_h), choice_h, vms_design_h),
         vms_design_i = ifelse(is.na(vms_design_i), choice_i, vms_design_i)) %>%
  mutate(vms_design_a = ifelse(is.na(vms_design_a), choice_item_to_be_ran, vms_design_a),
         vms_design_b = ifelse(is.na(vms_design_b), choice_item_to_be_ran_1, vms_design_b),
         vms_design_c = ifelse(is.na(vms_design_c), choice_onboard_electr, vms_design_c),
         vms_design_d = ifelse(is.na(vms_design_d), choice_text_messaging, vms_design_d),
         vms_design_e = ifelse(is.na(vms_design_e), choice_detailed_track, vms_design_e),
         vms_design_f = ifelse(is.na(vms_design_f), choice_opportunities_, vms_design_f),
         vms_design_g = ifelse(is.na(vms_design_g), choice_reduce_illegal, vms_design_g),
         vms_design_h = ifelse(is.na(vms_design_h), choice_increase_in_th, vms_design_h),
         vms_design_i = ifelse(is.na(vms_design_i), choice_full_data_repo, vms_design_i)) %>% 
  mutate(vms_design = ifelse(is.na(vms_design), q1st_choice, vms_design)) %>% 
  select(survey_id, vms_design_a:vms_design_i)
```


20. Combining all seasons, what are your top three targeted fisheries?
1.
2.
3.

```{r}
targetsp_df<-survey %>% 
  mutate(target_species_one = ifelse(is.na(targetone), target_species_one, targetone),
         target_species_two = ifelse(is.na(targettwo), target_species_two, targettwo),
         target_species_three = ifelse(is.na(targetthree), target_species_three, targetthree)) %>% 
  select(survey_id, target_species_one, target_species_two, target_species_three)
```

21. What percent of the total catch (out of 100%) goes to...
a. Own/household consumption
b. Shared to neighboring household
c. Traded in local market
d. Export
e. Other _______________________

```{r}
pc_names<-c("survey_id", "fraction_personal",	"fraction_neighbor",	"fraction_local_trade",	"fraction_export",	"fraction_other",	"other_fraction")

pc_a<-survey %>% 
  select(survey_id, fraction_personal:fraction_other) %>% 
  filter(survey_id < 7000 & survey_id > 4000)

pc_b<-survey %>% 
  select(survey_id, personal:other_21) %>% 
  filter(survey_id > 7000 | survey_id < 4000)

colnames(pc_a)<-pc_names
colnames(pc_b)<-pc_names
pct_catch<-rbind(pc_a, pc_b)
```

22. Are you part of a fishing organization?
◯	Yes
◯	No
If you selected Yes in Question 22, please answer Question 23-25
23. What type of organization?
◯	a. Cooperative 
◯	b. Union 
◯	c. Customary Organization (e.g. indigenous community) 
◯	d. Other _______________________
24. What role do you have in the organization?
◯	a. Apprentice
◯	b. Partner
◯	c. Director
◯	d. Other _______________________
25. How many members are in your fishing organization? 

```{r}
org_names<-c("survey_id",	"fishing_organization",	"fishing_org_type",	"other_type",	"fishing_org_role",	"other_role",	"fishing_org_members")

org_a<-survey %>% 
  select(survey_id,	fishing_organization,	fishing_org_type,	fishing_org_type_other,	fishing_org_role,	other_24,	fishing_org_members) %>%
  filter(survey_id < 7000 & survey_id > 4000)
  

org_b<-survey %>% 
  select(survey_id, q22m,	q23m,	other_23,	q24g,	other_24,	q25g) %>% 
  filter(survey_id > 7000 | survey_id < 4000)

colnames(org_a)<-org_names
colnames(org_b)<-org_names
organization<-rbind(org_a, org_b)
```


26. Who is allowed to fish for your #1 targeted fishery? (Select all that apply)
◯	a. Members of your fishing organization/ community only
◯	b. Members from you and neighboring fishing organization/ communities
◯	c. Anyone with a fishing permit
◯	d. There are no restrictions to access
◯	e. Other _______________________
27. What regulations exist for your #1 targeted fishery? (Select all that apply)
⬜	a. Gear Restrictions
⬜	b. Size Restrictions
⬜	c. Seasonal Restrictions
⬜	d. Spatial Restrictions
⬜	e. Quotas
⬜	f. Other  _______________________
⬜	g. None
28. Who is responsible for enforcement in your community? (Select all that apply)
⬜	a. Community Members
⬜	b. Village customary leader
⬜	c. Village Government
⬜	d. Provincial Government
⬜	e. National Government
⬜	f. No Enforcement
⬜	g. Other _______________________
29. On average, how often are these fishing regulations enforced?
◯	a. Every week
◯	b. Once a month
◯	c. A few times per year
◯	d. Once a year
◯	e. Never
30. How severe is the punishment when a person gets caught violating the fishing regulations?
◯	a. No Punishment
◯	b. Weak
◯	c. Moderate
◯	d. Strong
◯	e. Severe
31. Are there any closed areas in your fishing area?
◯	Yes
◯	No


```{r}
rules_a<-survey %>% 
  select(survey_id,
         access_target_species:mpa) %>% 
  filter(survey_id > 4000 & survey_id < 7000) %>% 
  select(survey_id,
         access_target_species	,
        access_target_species_other	,
        restriction_restriction_gear	,
        restriction_restriction_size	,
        restriction_restriction_season	,
        restriction_restriction_spacial	,
        restriction_restriction_quota	,
        restriction_other_restriction	,
        restriction_restriction_none	,
        restriction_other	,
        enforcement_enforcement_community_members	,
        enforcement_enforcement_village_leader	,
        enforcement_enforcement_village_gov	,
        enforcement_enforcement_provincial_gov	,
        enforcement_enforcement_national_gov	,
        enforcement_enforcement_none	,
        enforcement_other_enforcement	,
        enforcement_other	,
        enforcement_interval	,
        enforcement_interval_other	,
        punishment_severity	,
        mpa)

rules_b<-survey %>% 
  select(survey_id,
         q26g:q31g) %>% 
  filter(survey_id > 7000 | survey_id < 4000) %>% 
  mutate(other_access = NA) %>% 
  select(survey_id, 
         q26g	,
         other_access ,
         q27g_a_Gear_Restrictions	,
         q27g_b_Size_Restrictions	,
        q27g_c_Seasonal_Restrictions	,
        q27g_d_Spatial_Restrictions	,
        q27g_e_Quotas	,
        q27g_other	,
        q27g_none	,
        other_27	,
        q28g_community_memb	,
        q28g_village_custom	,
        q28g_village_govern	,
        q28g_provincial_gov	,
        q28g_national_gover	,
        q28g_no_enforcement	,
        q28g_other	,
        other_28	,
        q29g	,
        other_29	,
        q30g	,
        q31g)

rule_names <- c("survey_id", "access_target_species",	"other_access",	"restriction_gear",	"restriction_size",	"restriction_season",	"restriction_spacial",	"restriction_quota",	"restriction_other",	"restriction_none",	"other_restriction",	"enforcement_community_members",	"enforcement_village_leader",	"enforcement_village_gov",	"enforcement_provincial_gov",	"enforcement_national_gov",	"enforcement_none",	"enforcement_other",	"other_enforcement",	"enforcement_interval",	"other_interval",	"punishment_severity",	"mpa")

colnames(rules_a)<-rule_names
colnames(rules_b)<-rule_names
rules<-rbind(rules_a, rules_b)
```


32. What do you think are the biggest problems your fishery faces?
1. 
2.
3.
33. How do you think the problems you mentioned can be solved?
1. 
2.
3.
34. Please rank the following problems. 
		a. Trash polluting the ocean	
		b. Illegal Fishing	
		c. Extreme Weather	
		d. Corruption of fishing authorities
35. In the last few years, the current fish catch has…		
◯	a. Declined a lot		
◯	b. Declined slightly		
◯	c. Stayed the same		
◯	d. Improved slightly		
◯	e. Improved a lot		

```{r}
problems<-survey %>% 
  select(survey_id, 
         c(116:121, 260:265), #problem & Solution 
         c(122:125, 266:269), #rank
         c(126, 270, 271)) %>% #catch trends
  mutate(fishery_problem_one = ifelse(is.na(problem_one), fishery_problem_one, problem_one),
         fishery_problem_two = ifelse(is.na(problem_two), fishery_problem_two, problem_two),
         fishery_problem_three = ifelse(is.na(problem_three), fishery_problem_three, problem_three)) %>% 
    mutate(fishery_solution_one = ifelse(is.na(solution_one), fishery_solution_one, solution_one),
         fishery_solution_two = ifelse(is.na(solution_two), fishery_solution_two, solution_two),
         fishery_solution_three = ifelse(is.na(solution_three), fishery_solution_three, solution_three)) %>%
  mutate(rank_one = ifelse(is.na(rank_one), q1st_choice_001, rank_one),
         rank_two = ifelse(is.na(rank_two), q2nd_choice, rank_two),
         rank_three = ifelse(is.na(rank_three), q3rd_choice, rank_three),
         rank_four = ifelse(is.na(rank_four), q4th_choice, rank_four)) %>% 
  mutate(catch_trends = ifelse(is.na(catch_trends), catch_trends_35, catch_trends), 
         catch_trends = ifelse(is.na(catch_trends), q35p, catch_trends)) %>% 
  select(survey_id, starts_with("fishery_problem"), starts_with("fishery_solution"), starts_with("rank_"), catch_trends)
```
36
37
38
```{r}
likert_names<-names(likert_a)

likert_a<-survey %>% 
  select(survey_id, opinion_a:satisfaction_c) %>% 
  filter(survey_id < 7000 & survey_id > 4000)

likert_b<-survey %>% 
  select(survey_id, Formal_stock_assessm_bly_manage_fisheries:other_38) %>% 
  filter(survey_id > 7000 | survey_id < 4000) %>% 
  mutate(ngo = ifelse(is.na(ngo), Non_Governmental_Organizations_001, ngo)) %>% 
  select(-Non_Governmental_Organizations_001, -other_38)

colnames(likert_b)<- likert_names

likert<-rbind(likert_a, likert_b)
```

39. What is your age?

40. How many years have you been fishing?

```{r}
years<-survey %>% 
  select(survey_id, c(151, 298, 152, 299)) %>% 
  mutate(age = ifelse(is.na(age), q39d, age),
         years_fishing = ifelse(is.na(years_fishing), q40d, years_fishing)) %>% 
  select(-q39d, -q40d)
```

41. What is your level of education? (Please choose one)

```{r}
#edu_col<- c(153:154, 300:307)

education_df<-survey %>% 
  select(survey_id, c(153:154, 300:307)) %>% 
  mutate(education = ifelse(is.na(education), q41d, education)) %>% 
  mutate(other_education = ifelse(is.na(education_other), qPlease_specify_other_002, education_other)) %>% 
  select(survey_id, education, other_education)
```

42. What is your average monthly income? (INR/MEX)

43. What percent (out of 100%) of your annual income comes from fishing?

44. What percent (out of 100%) of your income is spent on fishing related expenses?

```{r}
income<-survey %>% 
  select(survey_id, income:income_percent_expenses, 
         q42d:                         q44_What_percent_ou_s_related_to_fishing) %>% 
  mutate(income = ifelse(is.na(income), q42d, income),
         income_fishing = ifelse(is.na(income_percent_fishing), q43_What_percent_ou_e_comes_from_fishing, income_percent_fishing), income_expenses = ifelse(is.na(income_percent_expenses), q44_What_percent_ou_s_related_to_fishing, income_percent_expenses)) %>% 
  select(survey_id, income, income_fishing, income_expenses)
  
```

```{r}
survey_final<- survey %>%
  select(start,	end,	survey_type,	survey_id,	survey_version,	interviewer,	country,	community,	sex) %>% 
  left_join(gear_df) %>% 
  left_join(vessel_df) %>% 
  left_join(tech_df) %>%
  left_join(fishtech_df) %>% 
  left_join(vms_text_df) %>% 
  left_join(ce_df) %>% 
  left_join(vms_goodbad_df) %>% 
  left_join(vms_design_df) %>% 
  left_join(targetsp_df) %>% 
  left_join(pct_catch) %>% 
  left_join(organization) %>% 
  left_join(rules) %>% 
  left_join(problems) %>%
  left_join(likert) %>% 
  left_join(years) %>% 
  left_join(education_df) %>% 
  left_join(income) 

names(survey_final)
```

```{r}


Any_additional_quest_comments_notes_etc, last_commends
```

